NIRCam Flux Calibration Plan

### 2017-03-24 ms.tex
I added a description and example of the spectrum rectification procedure I created.

\section{Spectral Typing of Candidate Analogs}
The Hectospec instrument on the MMT \citep{fabricant2005hectospec,mink2007hectoFibers} was used to obtain spectra of candidate solar analogs in the clusters .

>>>>

\clearpage
\section{Spectral Typing of Candidate Analogs}
The Hectospec instrument on the MMT \citep{fabricant2005hectospec,mink2007hectoFibers} was used to obtain spectra of candidate solar analogs in the clusters .
We processed the data with the standard IDL routine \texttt{hsred}\footnote{https://www.mmto.org/node/536}

We normalized the raw spectra output from \texttt{hsred} in order to pass it to a spectral rectification program \texttt{mkclass} \citep{gray2014classification}.
The first step in the normalization was to get an approximately normalized curve from the strongly curved spectrum shown in Figure \ref{fig:SpecRect}.
We fit an 8th order polynomial in log space to the flux as a function of wavelength.
It is important to do the fit in log-space because in linear space there are regions (near 3800 $\AA$) where the flux drops to low values and the fit can have zero crossings.
The resulting model (fit in linear space) results large negative values or NaNs when divided by the model, whereas the fit in log-space has no zero-crossings.
The polynomial fit is done piecewise in 3 equally spaced regions to take on small scale curvature.

The second step in the spectral rectification process is to normalize by the pseudo continuum and remove any residual curvature.
This is again fit with an 8th order polynomial in a piecewise fashion in three equally spaced wavelength chunks.
The modification for the second step is to do it in linear space (now that zero crossings will not occur) and also select only points greater than 1.0 to ensure they are continuum points.
The two steps (with polynomial fits) and final resulting spectrum are shown for an example source in Figure \ref{fig:SpecRect}.

\begin{figure}[!hbtp]
\centering
\includegraphics[width=.7\columnwidth]{O_0738209_p2134_rectification.pdf}
\caption{The spectral rectification process happens in two steps 1) take out the strong curvature with a piecewise polynomial in log flux space (top panel) and 2) fit the points above 1.0 with a new piecewise polynomial in linear flux space.}\label{fig:SpecRect}
\end{figure}
